### 2012-09-03 inst/examples/figure3.Rmd
change interpolation

ggplot(policy) + geom_line(aes(stock, stock-x_grid[value], color=variable))
dt <- data.table(policy)
linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,150, length=20)), by=variable]
ggplot(linear) + geom_line(aes(x,y,color=variable))
#  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
	#geom_smooth(aes(stock, stock-x_grid[value], color=variable)) 
```

>>>>

ggplot(policy) + geom_line(aes(stock, stock-x_grid[value], color=variable))
dat <- subset(policy, stock < 120)
dt <- data.table(dat)
linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,150, length=15)), by=variable]
ggplot(linear) + geom_smooth(aes(x,y,color=variable))
#  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
	#geom_smooth(aes(stock, stock-x_grid[value], color=variable)) 
```
